How and Why to run a Hack Week

### 2017-09-25 sections/design.tex
Added sentence about impostor syndrome to design section
added a couple of additional sentences about space in response to Laura's comments

A hackweek requires a flexible workspace environment with ample opportunity for re-configuration. 
Participants must have access to rooms that can accommodate lectures combined with interactive exchanges and individual work on laptops. 
Workspaces must also accommodate interactive project work where small teams can gather and work together uninterrupted by other groups.    
Universities are an obvious first choice for hosting a hack week given their access to scientific resources, research support and infrastructure. 
However traditional university lecture halls often do not meet the hack week criteria for interactive exchanges.
Fortunately active learning teaching methods are creating new environments that foster interactivity through modified seating arrangements and integration of computer monitors at group workstations.

@@

Hack week outcomes depend strongly on the interest and engagement of participants.
Some attendees, usually those with a strong background in hackathons and their specific topic of study, arrive with the goal of writing a scientific article.
Other attendees plan to learn a specific topic, such as machine learning, or to analyze a specific data set that relates to the tools covered in the tutorials.
This leads to a wide variety of project types from sandbox-style explorations to focused work efforts.
This breadth of possible outcomes makes it difficult to design for all possible participant goals, and calls for adaptive, flexible leadership among hack week organizers.

>>>>

A hackweek requires a flexible workspace environment with ample opportunity for re-configuration. 
Participants must have access to rooms that can accommodate lectures combined with interactive exchanges and individual work on laptops. 
Workspaces must also accommodate interactive project work where small teams can gather and work together uninterrupted by other groups.    
Universities are an obvious first choice for hosting a hack week given their access to scientific resources, research support and infrastructure. 
However traditional university lecture halls often do not meet the hack week criteria for interactive exchanges.
Fortunately active learning teaching methods are creating new environments that foster interactivity through modified seating arrangements and integration of computer monitors at group workstations. There is a natural tension between keeping the group together and providing physically separated break-out spaces. On the one hand, conducting the workshop in a single large venue improves group cohesion and prevents self-segregation of researchers and ideas. On the other hand, the interactive nature of the workshop may lead to an environment where it is difficult for individuals to focus on the highly complex tasks that are typical for hack week projects. It may hence be advisable to allow for diffusion of the group into adjacent rooms, while providing ample venue for the entire group to congregate for tutorials, breaks and reports.

@@

Hack week outcomes depend strongly on the interest and engagement of participants.
Some attendees, usually those with a strong background in hackathons and their specific topic of study, arrive with the goal of writing a scientific article.
Other attendees plan to learn a specific topic, such as machine learning, or to analyze a specific data set that relates to the tools covered in the tutorials.
This leads to a wide variety of project types from sandbox-style explorations to focused work efforts.
This breadth of possible outcomes makes it difficult to design for all possible participant goals, and calls for adaptive, flexible leadership among hack week organizers.
The large variety in participant backgrounds and experiences can lead to an increase in the prevalence of impostor syndrome experienced by many participants (see also supplementary materials), and it 
is important to take this into account during workshop design.
